Screening harmonies

### 2020-06-04 choosing_harmonies_Normal.Rmd
choosing threshold update

|  facets/distances	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|------------------	|------	|------	|------	|----	|----	|------	|
| d_1              	| d_11 	| d_12 	| d_13 	| .. 	| .. 	| d_1K 	|
| d_2              	|      	|      	|      	|    	|    	|      	|
| d_3              	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| d_m              	| d_m1 	| d_m2 	| d_m3 	| .. 	| .. 	| d_mL 	|

$H_{01}: d_{11} = d_{21} = \ldots = d_{m1} = 0$  
$H_{02}: d_{12} = d_{22} = \ldots = d_{L2} = 0$  
\vdots
$H_{0m}: d_{1m} = d_{2m} = \ldots = d_{Lm} = 0$

@@

```{r}
library(readr)
smart_normal <- read_rds("data/ smart_harmony_normal.rds")  %>% mutate(rank_normal = row_number())

@@

```{r, echo = FALSE}
p1 <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal() + 
  ggtitle("Rank 1 Section 6.1.1")  + 
  scale_x_discrete(breaks = seq(0, 23, 5))

p2 <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("") + ggtitle("") + ylab("")+ 
  theme_minimal() + 
  ggtitle("Rank 1 Section 6.1.2") + scale_x_discrete(labels = c('wday','wend'))

```{r, echo = FALSE}
p3 <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("week_month",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal() + 
  ggtitle("Rank 2 Section 6.1.2") + 
  scale_x_discrete(breaks = seq(0, 23, 5))

p4 <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "week_month",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("week of the month") + ggtitle("") + ylab("")+ 
  theme_minimal()  + 
  ggtitle("Rank 2 Section 6.1.2")

ggpubr::ggarrange(p1, p2,  ncol = 2)

ggpubr::ggarrange(p3, p4,  ncol = 2)
```

```{r}
smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot( gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot")

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot(gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot")

@@

@@

```{r}
cricket_data <- read_rds("data/cricket_data.rds")

@@

```{r}
cricket_data <- read_rds("data/cricket_data.rds")
cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
```

>>>>

|  facets/distances	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_K  	|
|------------------	|------	|------	|------	|----	|----	|------	|
| d_1              	| d_11 	| d_12 	| d_13 	| .. 	| .. 	| d_1K 	|
| d_2              	|      	|      	|      	|    	|    	|      	|
| d_3              	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| ..               	|      	|      	|      	|    	|    	|      	|
| d_m              	| d_m1 	| d_m2 	| d_m3 	| .. 	| .. 	| d_mK 	|

$H_{01}: d_{11} = d_{21} = \ldots = d_{m1} = 0$  
$H_{02}: d_{12} = d_{22} = \ldots = d_{m2} = 0$  
\vdots
$H_{0K}: d_{1K} = d_{2K} = \ldots = d_{mK} = 0$

@@

```{r allgraph}
library(readr)
smart_normal <- read_rds("data/ smart_harmony_normal.rds")  %>% mutate(rank_normal = row_number())

@@

```{r, echo = FALSE}
smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal() + 
  scale_x_discrete(breaks = seq(0, 23, 5))

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot( gran1 = "day_week", gran2 = "day_month", plot_type = "boxplot") + scale_x_discrete(breaks = seq(0, 31, 5))

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>% prob_plot(gran1 = "wknd_wday", gran2 = "day_month", plot_type = "boxplot") + scale_x_discrete(breaks = seq(0, 31, 5))

@@

smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot",
    #symmetric = TRUE,
    #quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("") + ggtitle("") + ylab("")+ 
  theme_minimal() + scale_x_discrete(labels = c('wday','wend'))

@@

```{r cricket}
cricket_data <- read_rds("data/cricket_data.rds")

@@

```{r cricket_lag}
cricket_data <- read_rds("data/cricket_data.rds")
cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
```
